---
title: My Thesis
author: You
output: 
  html_document:
bibliography: bibliography/bibliography.bib
abstract: >-
  This is a sample thesis that we're using to showcase some practical
  applications of integrated documents.
keywords: 'thesis, science, stuff'
linenumbers: true
---

# Our Sample Thesis

## Knitting your Thesis

Open this `Rmd` file in RMarkdown. It should all be ready to go, to turn it into a cool `HTML` document. To do that, look at the RStudio toolbar and click the `knit` button.

You can also knit (or render) your RMarkdown documents using the command line. There are good reasons for doing this, and cool tricks you can try (see the Tips & Tricks later in the workshop). To do that, go to the folder that your RMarkdown document is in and type in the command:

```
Rscript -e "rmarkdown::render('filename.Rmd')"
```

No need to try it here, but just wanted to mention it :)

## Integrating Code

When you're working on your thesis you're probably loading some data, and then doing some analysis. We're going to show a couple ways of doing it, but we're also going to look at how to integrate that code directly into your text.

### Data Import

We did some work looking at Github repositories earlier, and added information to a Google spreadsheet. I've downloaded the data into a CSV file in the `data/input` directory of this project.

```{r}
table <- read.csv('data/input/GitHubRepos.csv')
```

Once the table is read in by the code block above we can say some things about it, for example, I can let you know that there are `r nrow(table)` rows in the table. I wanted to know how many of the tables had `README` files. There are `r sum(table[,3] == 'yes', na.rm=TRUE)` README files, out of `r sum(table[,3] == '')` repositories sampled. **The fact that we sampled no repositories at all is pretty telling.**

```{r}
plot(factor(table[,3]))
```

# Templates

Most universities and departments make a Word or latex template available for theses. For example, the [template in the `templates` folder](templates/thesistemplate.docx) is provided by [Simon Fraser University](https://www.lib.sfu.ca/help/publish/thesis/templates).

# Bibliography

Pandoc (and by extension, RMarkdown) can support the use of a bibliography in [Bibtex format](http://www.bibtex.org/). These references can be rendered into a number of different formats using an XML-type file called the [Citation Style Language](https://citationstyles.org/), or CSL. These files define how the reference is rendered and referenced in text. You can see a full list of available formats (for a large number of journals) in the [CSL Github styles repository](https://github.com/citation-style-language/styles).

If I wanted to cite a paper, for example, the winner of an IgNobel prize for making feces knives [@eren2019experimental], I could simply add an in text citation to my bibliography file. We'll edit this further once we get used to using `git` workflows.

There's some great information about [using RMarkdown citations & bibliographies](https://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html) on the RStudio website.

# References
